---
title: "Bayes_testing"
author: "Emma Beekman"
date: "`r Sys.Date()`"
output: pdf_document
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, MESSAGE = FALSE)
```
Necessary libraries: 
```{r}
library(bnlearn)
library(dagitty)
library(lavaan)
library(bayesianNetworks)
library(dplyr)
```

# Loading and plotting our DAG
Load the data, and save it as d.

```{r}
d <- read.csv(file = 'online_shoppers_intention.csv')
```

Make our causal diagram, and save it as g.

```{r}
g <- dagitty('
dag {
bb="-2.798,-5.782,3.54,4.734"
Administrative_Duration [pos="1.676,-3.408"]
Informational_Duration [pos="1.643,-5.374"]
ProductRelated_Duration [pos="2.481,-3.739"]
Revenue [pos="3.239,-0.278"]
SpecialDay [pos="-0.357,-0.295"]
VisitorType [pos="0.614,-4.355"]
Weekend [pos="-0.350,-2.945"]
Administrative_Duration -> ProductRelated_Duration
Informational_Duration -> ProductRelated_Duration
ProductRelated_Duration -> Revenue
SpecialDay -> ProductRelated_Duration
SpecialDay -> Revenue
SpecialDay -> VisitorType
VisitorType -> Administrative_Duration
VisitorType -> Informational_Duration
VisitorType -> ProductRelated_Duration
VisitorType -> Revenue
Weekend -> Revenue
Weekend -> VisitorType
}
             ')
```

Plot our DAG

```{r}
plot(g)
```
Show the list of conditional independencies that are implied by the diagram. 

```{r}
impliedConditionalIndependencies(g)
```

# Testing: Combination of Categorical and continuous data
(Following https://currentprotocols.onlinelibrary.wiley.com/doi/10.1002/cpz1.45 Basic Protocol 4)
This approach only works for ordinal categorical variables. It can also be used with binary variables because binary variables can be given an arbitrary ordering. 

Define binary variables. 
```{r}
d$Weekend <- as.integer(d$Weekend) #True is 1, False is 2
d$Revenue <- as.integer(d$Revenue) #True is 1, False is 2
```
Not sure if we should do this, but current work-around to handle VisitorType since it contains 3 variables. VisitorType has 3 categories: new, returning and other. I removed 'other' for now. 

```{r}
d <- d %>%
  filter(VisitorType != "Other")

d$VisitorType <- as.integer(as.factor(d$VisitorType))
```


Compute the correlation matrix. And test the implied conditional independencies of the model structure against the correlation matrix. 
```{r}
corr <- lavCor(d)
localTests(g, sample.cov=corr, sample.nobs=nrow(d))
# write.csv(init_test, "Report\\init_test.csv", row.names = TRUE)
```
Plot the test results. Ideally, all effect sizes should fall onto the 0 line. 

```{r}
plotLocalTestResults(localTests(g, sample.cov=corr, sample.nobs=nrow(d)))
```
Ad_D indep of In_D | VstT is very unlikely so we decide to make these dependent. This results in the following DAG: 

```{r}
g2 <- dagitty('
dag {
bb="-2.798,-5.782,3.54,4.734"
Administrative_Duration [pos="1.676,-3.408"]
Informational_Duration [pos="1.643,-5.374"]
ProductRelated_Duration [pos="2.481,-3.739"]
Revenue [pos="3.239,-0.278"]
SpecialDay [pos="-0.357,-0.295"]
VisitorType [pos="0.614,-4.355"]
Weekend [pos="-0.350,-2.945"]
Administrative_Duration -> ProductRelated_Duration
Informational_Duration -> Administrative_Duration
Informational_Duration -> ProductRelated_Duration
ProductRelated_Duration -> Revenue
SpecialDay -> ProductRelated_Duration
SpecialDay -> Revenue
SpecialDay -> VisitorType
VisitorType -> Administrative_Duration
VisitorType -> Informational_Duration
VisitorType -> ProductRelated_Duration
VisitorType -> Revenue
Weekend -> Revenue
Weekend -> VisitorType
}
             ')

plot(g2)
```
```{r}
corr <- lavCor(d)
localTests(g2, sample.cov=corr, sample.nobs=nrow(d))
```
```{r}
plotLocalTestResults(localTests(g2, sample.cov=corr, sample.nobs=nrow(d)))
```
This improved the results a lot. We can do the same for Ad_D indep of SpcD | VstT: 

```{r}
g3 <- dagitty('
dag {
bb="-2.798,-5.782,3.54,4.734"
Administrative_Duration [pos="1.676,-3.408"]
Informational_Duration [pos="1.643,-5.374"]
ProductRelated_Duration [pos="2.481,-3.739"]
Revenue [pos="3.239,-0.278"]
SpecialDay [pos="-0.357,-0.295"]
VisitorType [pos="0.614,-4.355"]
Weekend [pos="-0.350,-2.945"]
Administrative_Duration -> ProductRelated_Duration
Informational_Duration -> Administrative_Duration
Informational_Duration -> ProductRelated_Duration
ProductRelated_Duration -> Revenue
SpecialDay -> Administrative_Duration
SpecialDay -> ProductRelated_Duration
SpecialDay -> Revenue
SpecialDay -> VisitorType
VisitorType -> Administrative_Duration
VisitorType -> Informational_Duration
VisitorType -> ProductRelated_Duration
VisitorType -> Revenue
Weekend -> Revenue
Weekend -> VisitorType
}

             ')

plot(g3)
```
```{r}
corr <- lavCor(d)
localTests(g3, sample.cov=corr, sample.nobs=nrow(d))
```
```{r}
plotLocalTestResults(localTests(g3, sample.cov=corr, sample.nobs=nrow(d)))
```

Again, it is an improvement. Now we can do the same for In_D indep SpcD | VstT: 
```{r}
g4 <- dagitty('
dag {
bb="-2.798,-5.782,3.54,4.734"
Administrative_Duration [pos="1.676,-3.408"]
Informational_Duration [pos="1.643,-5.374"]
ProductRelated_Duration [pos="2.481,-3.739"]
Revenue [pos="3.239,-0.278"]
SpecialDay [pos="-0.357,-0.295"]
VisitorType [pos="0.614,-4.355"]
Weekend [pos="-0.350,-2.945"]
Administrative_Duration -> ProductRelated_Duration
Informational_Duration -> Administrative_Duration
Informational_Duration -> ProductRelated_Duration
ProductRelated_Duration -> Revenue
SpecialDay -> Administrative_Duration
SpecialDay -> Informational_Duration
SpecialDay -> ProductRelated_Duration
SpecialDay -> Revenue
SpecialDay -> VisitorType
VisitorType -> Administrative_Duration
VisitorType -> Informational_Duration
VisitorType -> ProductRelated_Duration
VisitorType -> Revenue
Weekend -> Revenue
Weekend -> VisitorType
}

             ')

plot(g4)
```
```{r}
corr <- lavCor(d)
localTests(g4, sample.cov=corr, sample.nobs=nrow(d))
# write.csv(localTest, "Report\\local_test.csv", row.names = TRUE)
```
```{r}
plotLocalTestResults(localTests(g4, sample.cov=corr, sample.nobs=nrow(d)))
```

Not all exactly on the middle line but should be good enough. 

# Fit a model based on the polychoric correlation matrix
```{r}
fit <- sem( toString(g4, "lavaan"), sample.cov = corr, sample.nobs = nrow(d))
summary(fit)
summary
# write.csv(sum, "Report\\summary_stat.csv", row.names = TRUE)
```
Original graph: 
```{r}
plot(g4)
```
graph with coefficients: 

```{r}
fg <- lavaanToGraph(fit, digits = 2)
cg <- coordinates(g4)
coordinates(fg) <- cg
plot(fg, show.coefficients=TRUE)
```
```{r}
library(lavaanPlot)
lavaanPlot(model = fit, coefs=TRUE, digits=3)
```
### Added after feedback: remove paths with high p-values

```{r}
summary(fit)
```

Removed path between productrelated_duration and special day

```{r}
g5 <- dagitty('
dag {
bb="0,0,1,1"
Administrative_Duration [pos="0.295,0.572"]
Informational_Duration [pos="0.391,0.453"]
ProductRelated_Duration [pos="0.538,0.697"]
Revenue [pos="0.584,0.834"]
SpecialDay [pos="0.250,0.073"]
VisitorType [pos="0.522,0.331"]
Weekend [pos="0.694,0.078"]
Administrative_Duration -> ProductRelated_Duration
Informational_Duration -> Administrative_Duration
Informational_Duration -> ProductRelated_Duration
ProductRelated_Duration -> Revenue
SpecialDay -> Administrative_Duration [pos="0.208,0.380"]
SpecialDay -> Informational_Duration
SpecialDay -> Revenue [pos="0.005,0.763"]
SpecialDay -> VisitorType
VisitorType -> Administrative_Duration [pos="0.300,0.317"]
VisitorType -> Informational_Duration
VisitorType -> ProductRelated_Duration
VisitorType -> Revenue [pos="0.715,0.573"]
Weekend -> Revenue [pos="0.998,0.575"]
Weekend -> VisitorType
}


')

plot(g5)


```
```{r}
corr <- lavCor(d)
localTests(g5, sample.cov=corr, sample.nobs=nrow(d))

```
```{r}

fit <- sem( toString(g5, "lavaan"), sample.cov = corr, sample.nobs = nrow(d))
summary(fit)
```
```{r}
plotLocalTestResults(localTests(g5, sample.cov=corr, sample.nobs=nrow(d)))
```
This is good, yes. Now remove weekend to revenue

```{r}
g6 <- dagitty('
dag {
bb="0,0,1,1"
Administrative_Duration [pos="0.295,0.572"]
Informational_Duration [pos="0.391,0.453"]
ProductRelated_Duration [pos="0.538,0.697"]
Revenue [pos="0.584,0.834"]
SpecialDay [pos="0.250,0.073"]
VisitorType [pos="0.522,0.331"]
Weekend [pos="0.694,0.078"]
Administrative_Duration -> ProductRelated_Duration
Informational_Duration -> Administrative_Duration
Informational_Duration -> ProductRelated_Duration
ProductRelated_Duration -> Revenue
SpecialDay -> Administrative_Duration [pos="0.208,0.380"]
SpecialDay -> Informational_Duration
SpecialDay -> Revenue [pos="0.005,0.763"]
SpecialDay -> VisitorType
VisitorType -> Administrative_Duration [pos="0.300,0.317"]
VisitorType -> Informational_Duration
VisitorType -> ProductRelated_Duration
VisitorType -> Revenue [pos="0.715,0.573"]
Weekend -> VisitorType
}

')

plot(g6)


```

```{r}
corr <- lavCor(d)
localTests(g6, sample.cov=corr, sample.nobs=nrow(d))

```

```{r}
fit <- sem( toString(g6, "lavaan"), sample.cov = corr, sample.nobs = nrow(d))
summary(fit)
```

```{r}
plotLocalTestResults(localTests(g6, sample.cov=corr, sample.nobs=nrow(d)))
```

```{r}
library(lavaanPlot)
lavaanPlot(model = fit, coefs=TRUE, digits=3)
```

## Tried to make the network more complicated
Added PageValues and BounceRates

```{r}
g7 <- dagitty('
dag {
bb="0,0,1,1"
Administrative_Duration [pos="0.295,0.572"]
BounceRates [pos="0.799,0.611"]
Informational_Duration [pos="0.391,0.453"]
PageValues [pos="0.682,0.271"]
ProductRelated_Duration [pos="0.538,0.697"]
Revenue [pos="0.559,0.874"]
SpecialDay [pos="0.250,0.073"]
VisitorType [pos="0.511,0.176"]
Weekend [pos="0.694,0.078"]
Administrative_Duration -> ProductRelated_Duration
BounceRates -> Revenue [pos="0.794,0.700"]
Informational_Duration -> Administrative_Duration
Informational_Duration -> ProductRelated_Duration
PageValues -> Administrative_Duration [pos="0.570,0.517"]
PageValues -> BounceRates
PageValues -> Informational_Duration
PageValues -> ProductRelated_Duration
ProductRelated_Duration -> Revenue
SpecialDay -> Administrative_Duration [pos="0.208,0.380"]
SpecialDay -> Informational_Duration
SpecialDay -> Revenue [pos="0.005,0.763"]
SpecialDay -> VisitorType
VisitorType -> Administrative_Duration [pos="0.300,0.317"]
VisitorType -> BounceRates
VisitorType -> Informational_Duration
VisitorType -> PageValues
VisitorType -> ProductRelated_Duration
VisitorType -> Revenue [pos="0.715,0.573"]
Weekend -> VisitorType
}


')

plot(g7)


```
```{r}
corr <- lavCor(d)
localTests(g7, sample.cov=corr, sample.nobs=nrow(d))

```
```{r}
plotLocalTestResults(localTests(g7, sample.cov=corr, sample.nobs=nrow(d)))
```
Added path from page value to revenue
```{r}
g8 <- dagitty('
dag {
bb="0,0,1,1"
Administrative_Duration [pos="0.295,0.572"]
BounceRates [pos="0.799,0.611"]
Informational_Duration [pos="0.391,0.453"]
PageValues [pos="0.682,0.271"]
ProductRelated_Duration [pos="0.538,0.697"]
Revenue [pos="0.559,0.874"]
SpecialDay [pos="0.250,0.073"]
VisitorType [pos="0.511,0.176"]
Weekend [pos="0.694,0.078"]
Administrative_Duration -> ProductRelated_Duration
BounceRates -> Revenue [pos="0.794,0.700"]
Informational_Duration -> Administrative_Duration
Informational_Duration -> ProductRelated_Duration
PageValues -> Administrative_Duration [pos="0.570,0.517"]
PageValues -> BounceRates
PageValues -> Informational_Duration
PageValues -> ProductRelated_Duration
PageValues -> Revenue [pos="0.717,0.549"]
ProductRelated_Duration -> Revenue
SpecialDay -> Administrative_Duration [pos="0.208,0.380"]
SpecialDay -> Informational_Duration
SpecialDay -> Revenue [pos="0.005,0.763"]
SpecialDay -> VisitorType
VisitorType -> Administrative_Duration [pos="0.300,0.317"]
VisitorType -> BounceRates
VisitorType -> Informational_Duration
VisitorType -> PageValues
VisitorType -> ProductRelated_Duration
VisitorType -> Revenue [pos="0.669,0.510"]
Weekend -> VisitorType
}
')

plot(g8)
```
```{r}
corr <- lavCor(d)
localTests(g8, sample.cov=corr, sample.nobs=nrow(d))

```

```{r}
plotLocalTestResults(localTests(g8, sample.cov=corr, sample.nobs=nrow(d)))
```

Added productrelated to bouncerate

```{r}
g9 <- dagitty('
dag {
bb="0,0,1,1"
Administrative_Duration [pos="0.295,0.572"]
BounceRates [pos="0.727,0.785"]
Informational_Duration [pos="0.391,0.453"]
PageValues [pos="0.682,0.271"]
ProductRelated_Duration [pos="0.538,0.697"]
Revenue [pos="0.541,0.985"]
SpecialDay [pos="0.250,0.073"]
VisitorType [pos="0.511,0.176"]
Weekend [pos="0.694,0.078"]
Administrative_Duration -> ProductRelated_Duration
BounceRates -> Revenue [pos="0.794,0.700"]
Informational_Duration -> Administrative_Duration
Informational_Duration -> ProductRelated_Duration
PageValues -> Administrative_Duration [pos="0.570,0.517"]
PageValues -> BounceRates
PageValues -> Informational_Duration
PageValues -> ProductRelated_Duration
PageValues -> Revenue [pos="0.717,0.549"]
ProductRelated_Duration -> BounceRates
ProductRelated_Duration -> Revenue
SpecialDay -> Administrative_Duration [pos="0.208,0.380"]
SpecialDay -> Informational_Duration
SpecialDay -> Revenue [pos="0.005,0.763"]
SpecialDay -> VisitorType
VisitorType -> Administrative_Duration [pos="0.300,0.317"]
VisitorType -> BounceRates
VisitorType -> Informational_Duration
VisitorType -> PageValues
VisitorType -> ProductRelated_Duration
VisitorType -> Revenue [pos="0.669,0.510"]
Weekend -> VisitorType
}

')

plot(g9)
```

```{r}
corr <- lavCor(d)
localTests(g9, sample.cov=corr, sample.nobs=nrow(d))

```
```{r}
plotLocalTestResults(localTests(g9, sample.cov=corr, sample.nobs=nrow(d)))
```

```{r}
fit <- sem( toString(g9, "lavaan"), sample.cov = corr, sample.nobs = nrow(d))
summary(fit)
```

```{r}
plot_coef = lavaanPlot(model = fit, coefs=TRUE, digits=3)
save_png(plot_coef, "Report\\dag_final.png")
```